---
title             : "A Pilot Study: Week 5 Lab 8 Done by Three Git Newbie Ducks "
# Haha! Great title!
shorttitle        : "w5lab8"

author: 
  - name          : "Heidi Shi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1248 University of Oregon Eugene, Oregon 97403-1248"
    email         : "hshi@uoregon.com"
  - name          : "Jeongim Jin"
    affiliation   : "1"
  - name          : "Jung-ah Lee"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"


abstract: |
 In recent years, Rstudio and Github have been widely regarded as one of the essential research tools for social science inquiries @srivastava2000web. Previous studies have revealed their significant methodological impact on disciplines such as psychology, linguistics, education and so forth (Shi & Jin, 2017; Lee 2018). This study is an attempt to solve all the questions listed in Week5 Lab8, one of the most challenging issues in the history of Fall 2018 EDLD 610 @morshedi1985optimal. Through a collaborative approach to lab 8, this study aims to show that Rstudio and Github are learnable, and sufficient training is one of the most efficient methods in R language acquisition @mobasher2000automatic.
  
# Great abstract!

# <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Lab8"

bibliography      : ["lab8-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5,
                      fig.height = 8)
library(rio)
library(here)
library(tidyverse)
library(janitor)
library("papaja")

theme_set(theme_minimal())
# I deleted the `base_size` argument because you shouldn't really need
# it here, and it makes the overall labels/legends smaller (When set to 8.
# You could also use it to make them bigger)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We used methods introduced by @pan2011. Besides we also adopted the diligent and collaborative approach to Rstudio (see @ahmed2001; @kadar2011).

## Participants
Cute ducks who are intersted in Rstudio, Female, n=3.

## Material
Rstudio, an Octopus app called "GitKraken", Github. 

## Procedure
We compared pre and post-training skills of Rstudio and Github. 

## Data analysis
We used @kadar2011 for all our analyses.


# Results

```{r Commit 2 Q3, echo=FALSE}
library(rio)
library(here)
star <- import(here("Star", "star.csv"))
```

```{r Commit 4 table, results ="asis"}
# head(star) # You don't want stuff like this in your doc when you're rendering because it will show up in your rendered file
library(tidyverse)
star %>%
  group_by(sex, frl) %>%
  summarize(mean = mean(tmathss),
            sd = sd(tmathss),
            mean = mean(treadss),
            sd = sd(treadss)) %>%
  knitr::kable(format = "latex",
               booktabs = TRUE, # make it pretty
               caption = "An amazing caption") # Add a caption so it shows up where it should
```

```{r fig.cap = "An awesome fig", echo = FALSE}

# star %>% 
#   mutate(frl = factor(frl)) # Also showing up in your output, so comment out/delete

theme_set(theme_minimal())
ggplot(star, aes(totexp, tmathss))+
  geom_point()+
  geom_smooth(method = "lm", aes(color = frl))+
  labs(x = "Teacher Experience(years)", 
       y = "Total Math Scale Score")

```



# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "lab8-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
