---
title             : "Lab9-Heidi-Jeongim-Jungah"
shorttitle        : "w5lab8"

author: 
  - name          : "Jungah-Lee"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1248 University of Oregon Eugene, Oregon 97403-1248"
    email         : "jlee27@uoregon.com"
  - name          : "Jeongim Jin"
    affiliation   : "2"
  - name          : "Heidi Shi"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
  - id            : "2"
    institution   : "University of Oregon"
  - id            : "3"
    institution   : "University of Oregon"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man, fleqn, noextraspace"
output            : papaja::lab9_html: toc: true
                    toc_depth: 4
                    toc_float: true
                    code_folding: "hide""
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants
The authors gathered teenagers who attend different schools in the U.S. 
## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

```{r echo = FALSE}
library(here)
library(rio)
eclsk_samp <- import(here("data", "ecls-k_samp.sav"))
View(eclsk_samp)
head(eclsk_samp)
```

```{r echo = FALSE}
View(eclsk_samp)
library(dplyr)
library(ggplot2)
eclsk_samp %>%
  characterize() %>%
  ggplot(eclsk_samp, aes(x=T1MSCALE, y=T2MSCALE) + 
           geom_point(color = "grey 70") + 
           geom_smooth(method="lm", se=FALSE, aes(color = SES_cat))+
           labs(x = "Math Score (time 1)", y = "Math Score (time 2)",
                title = "Math scores", subtitle = "Relation from Time 1 to Time 2")
```
# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
