---
title             : "Lab9-Heidi-Jeongim-Jungah"
shorttitle        : "w5lab9"

author: 
  - name          : "Jungah-Lee"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1248 University of Oregon Eugene, Oregon 97403-1248"
    email         : "jlee27@uoregon.com"
  - name          : "Jeongim Jin"
    affiliation   : "2"
  - name          : "Heidi Shi"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
  - id            : "2"
    institution   : "University of Oregon"
  - id            : "3"
    institution   : "University of Oregon"

authornote: |
  Jung-ah Lee joined the Department of East Asian Langauges and Literatures at the Unviersity of Oregon at 2017.


abstract: |
 This article provides an introduction to this issue of Language in Society by  exploring the relationship of the concept of Community of Practice (CofP)  to related terms and theoretical frameworks. The criterial characteristics and  constitutive features of a CofP are examined; the article points out how a  CofP framework is distinguished from other sociolinguistic and social psy-  chological frameworks, including social identity theory, speech community,  social network and social constructionist approaches. (Community of Practice, speech community, gender, sex, social practice, ethnographic sociolinguistics, discourse analysis)
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Community of Practice, Language Socialization"
wordcount         : "X"

bibliography      : ["lab9-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man, fleqn, noextraspace"
output            : 
                   papaja::apa6_pdf:
                     toc: true
                     toc_depth: 4
                    
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5,
                      fig.height = 8)
library(rio)
library(here)
library(tidyverse)
library(janitor)
library("papaja")

theme_set(theme_minimal(base_size = 8))

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


\newpage

# **Methods**
We adopted the method introduced by @pan2011, the author of *Phonetics and phonology of Nantong Chinese*We used methods introduced by @ahmed2001. Besides we also adopted the diligent and collaborative approach to Rstudio (see @kadar2011).

## *Participants*
The authors gathered teenagers who attend different schools on the Pacific Northwest, *Eugene,Oregon*.

### Males###
n=4

### Females###
n=4

####Female Subjects from High School A####
n=2

####Female Subjects from High School B####
n=2

## *Material*

## *Procedure*

## *Data analysis*
We used @pan2011 for all our analyses.

```{r Question3, echo = FALSE}
library(rio)
library(here)
eclsk_samp <- import(here("data", "ecls-k_samp.sav"))
```


$$
math_t2i = \alpha + \beta_1(math_t1i) + \beta_2(SES_cat1) + \beta_3(math_t1i x SES_cat1)\epsilon 
$$
  

```{r Question5, echo = FALSE}

library(tidyverse)
library(dplyr)
library(ggplot2)
ggplot(eclsk_samp, aes(x = T1MSCALE, y = T2MSCALE)) +
  geom_point(color = "grey 70") +
  geom_smooth(method = "lm", se = FALSE, aes(color = SES_cat)) +
  labs(x = "Math Score (time 1)",
       y = "Math Score (time 2)",
       title = "Math scores",
       subtitle = "Relation from Time 1 to Time 2")

```

# **Results**
Therefore, it is found that the math scores of su

# **Discussion**


\newpage

# **References**
```{r create_r-references}
r_refs(file = "lab9-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
